---
title: "Sample Quarto Presentation"
subtitle: "With Python and R Code Examples"
author: "Your Name"
format:
  revealjs:
    theme: dark
    slide-number: true
    chalkboard: true
    preview-links: auto
---

## Introduction

This is a sample Quarto presentation demonstrating:

- Python code execution
- R code execution
- Mixed language support

## Python Example

```{python}
#| echo: true
import matplotlib.pyplot as plt
import numpy as np

# Generate data
x = np.linspace(0, 10, 100)
y = np.sin(x)

# Create plot
plt.figure(figsize=(8, 4))
plt.plot(x, y, 'b-', linewidth=2)
plt.title('Sine Wave')
plt.xlabel('X')
plt.ylabel('Y')
plt.grid(True)
plt.show()
```

## Python Data Analysis

```{python}
#| echo: true
import pandas as pd

# Create sample data
data = {
    'Name': ['Alice', 'Bob', 'Charlie', 'David'],
    'Score': [85, 92, 78, 95],
    'Grade': ['B', 'A', 'C', 'A']
}

df = pd.DataFrame(data)
print(df)
print(f"\nAverage Score: {df['Score'].mean():.2f}")
```

## R Example

```{r}
#| echo: true
library(ggplot2)

# Create sample data
data <- data.frame(
  x = 1:10,
  y = rnorm(10)
)

# Create plot
ggplot(data, aes(x = x, y = y)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 3) +
  theme_minimal() +
  labs(title = "Random Data Plot", x = "Index", y = "Value")
```

## R Data Summary

```{r}
#| echo: true
# Create sample dataset
iris_summary <- iris |>
  subset(Species == "setosa") |>
  summary()

print(iris_summary)
```

## Mixed Workflow

You can use both languages in the same presentation:

1. Load data in R
2. Analyze it with Python
3. Visualize with either language

This flexibility makes Quarto ideal for data science presentations!

## Getting Started

To render this presentation:

```bash
quarto render example-presentation.qmd
```

Or to preview with live reload:

```bash
quarto preview example-presentation.qmd
```

## Thank You!

Questions?

---

**Resources:**

- [Quarto Documentation](https://quarto.org)
- [Quarto Presentations Guide](https://quarto.org/docs/presentations/)
