---
title: "Computational Reproducibility in Data Science"
subtitle: "With Python and R Code Examples"
author: "Venustiano Soancatl Aguilar"
format:
  revealjs:
    theme: dark
    slide-number: true
    chalkboard: true
    preview-links: auto
---

## Goal

Computational reproducibility means that research results obtained through computation can be consistently `re-produced` by others  given the same inputs and methods. 



## The Pillars

- Code
- Data
- `Environment`
- Documentation
- Workflows

## The Challenges

- Software rot
- Data availability
- Complexity
- Human factors

## Benefits of Computational Reproducibility

1. Integrity and Trust
2. `Efficiency and Reuse`
3. Collaboration and Transparency
4. `Long-term` Preservation
5. Scalability and Generalization
6. Policy and Funding Compliance


## R Example

```{r}
#| echo: true
library(ggplot2)

# Create sample data
data <- data.frame(
  x = 1:10,
  y = rnorm(10)
)

# Create plot
ggplot(data, aes(x = x, y = y)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "red", size = 3) +
  theme_minimal() +
  labs(title = "Random Data Plot", x = "Index", y = "Value")
```

## R Data Summary

```{r}
#| echo: true
# Create sample dataset
iris_summary <- iris |>
  subset(Species == "setosa") |>
  summary()

print(iris_summary)
```

## Mixed Workflow

You can use both languages in the same presentation:

1. Load data in R
2. Analyze it with Python
3. Visualize with either language

This flexibility makes Quarto ideal for data science presentations!

## Getting Started

To render this presentation:

```bash
quarto render example-presentation.qmd
```

Or to preview with live reload:

```bash
quarto preview example-presentation.qmd
```

## Thank You!

Questions?

---

**Resources:**

- [Quarto Documentation](https://quarto.org)
- [Quarto Presentations Guide](https://quarto.org/docs/presentations/)
